---
title: "Data Description"
output: github_document
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)
set.seed(923)
csvdir <- "~/Dropbox/Quimica/Docker/docker-solubility/data_analysis/data/edited/"
library("tidyverse")
library("readr")
library("broom")
library("kableExtra")
umbralLogS <- log(0.3, base = 10)
train_percent <- 0.6
test_percent  <- 0.2 
```

## Data Description

Data is available as [`Complete_dataset_without_duplicates`](https://raw.githubusercontent.com/RodrigoZepeda/docker-solubility/master/data_analysis/data/edited/Complete_dataset_without_duplicates.csv) on Github. 

```{r, message=FALSE}
mysol <- read_csv("https://raw.githubusercontent.com/RodrigoZepeda/docker-solubility/master/data_analysis/data/edited/Complete_dataset_without_duplicates.csv")
```

In log solubility, the variables include:
```{r}
myvars <- length(which(mysol$logS > umbralLogS)) 
mysum <- summary(mysol$logS)
kable(tidy(mysum), digits = 3)  
```

Of which `r myvars` out of `r nrow(mysol)` (representing `r round(myvars/nrow(mysol)*100,2)` %) are above the solubility threshold of $\log S >$ `r round(umbralLogS,2)`. For those variables their distribution is:

```{r}
mysum <- summary(mysol$logS[which(mysol$logS > umbralLogS)])
kable(tidy(mysum), digits = 3)  
```

The overall (adjusted) distribution is shown by the following kernel density:
```{r}
ggplot(mysol, aes(x = logS)) + 
  geom_histogram(aes(y = ..density..), bins = 100, fill = "#628078") +
  geom_density(color = "#ff3a22", size = 1) + 
  theme_classic() +
  geom_vline(aes(xintercept = umbralLogS), size = 1, color = "#a4893d",
             linetype = "dotted") +
  xlab("Log Solubility (logS)") +
  ylab("Density") + 
  ggtitle("Log Solubility dataset description.") +
  annotate("text", x = umbralLogS + 1, y = 0.2, label = "Solubility\nthreshold", color = "#a4893d") 
```

```{r}
#Generate soluble datasrt
mysol[, "Category"] <- "no soluble"
mysol[which(mysol$logS > umbralLogS), "Category"] <- "soluble"
write.csv(mysol, paste0(csvdir,"Complete_dataset_without_duplicates_with_categories.csv"), row.names = FALSE)
```

We generated `train`, `test` and `validate` datasets which have the following characteristics

```{r}
mysol    <- mysol %>% mutate(id = row_number())
train    <- mysol %>% sample_frac(train_percent)
test     <- anti_join(mysol, train, by = 'id')
validate <- test %>% sample_frac(test_percent/(1 - train_percent))
test     <- anti_join(test, validate, by = "id")

mytrain <- summary(train$logS)
mytest  <- summary(test$logS)
myvalid <- summary(validate$logS)

mysummaries <- as.data.frame(rbind(mytrain, mytest, myvalid),
                             row.names = c("Train","Test","Validate"))

mysummaries$`Percent Soluble` <- c(
  length(which(train$logS > umbralLogS))/nrow(train)*100,
  length(which(test$logS > umbralLogS))/nrow(test)*100,
  length(which(validate$logS > umbralLogS))/nrow(validate)*100)

mysummaries$`Number of Molecules` <- c(nrow(train), nrow(test), nrow(validate))

kable(mysummaries, digits = 3)

```

With adjusted kernel densities for their log solubilities as follows:
```{r}
ggplot(mapping = aes(x = logS, y = ..density..)) + 
  geom_density(data = train, aes(color = "Train"), size = 1) + 
  geom_density(data = test, aes(color = "Test"), size = 1) + 
  geom_density(data = validate, aes(color = "Validate"), size = 1) + 
  theme_classic() +
  geom_vline(aes(xintercept = umbralLogS), size = 1, color = "#a4893d",
             linetype = "dotted") +
  xlab("Log Solubility (logS)") +
  ylab("Density") + 
  ggtitle("Log Solubility dataset description.") +
  annotate("text", x = umbralLogS + 1, y = 0.2, label = "Solubility\nthreshold", color = "#a4893d") + 
  scale_color_manual("Dataset", 
                     values = c("Train" = "#628078", 
                                "Test" = "#ff3a22",
                                "Validate" = "deepskyblue3")) +
  theme(legend.position = "bottom")
```

```{r}
write.csv(train, paste0(csvdir,"TRAIN_Complete_dataset_without_duplicates_with_categories.csv"), row.names = FALSE)
write.csv(test, paste0(csvdir,"TEST_Complete_dataset_without_duplicates_with_categories.csv"), row.names = FALSE)
write.csv(validate, paste0(csvdir,"VALIDATE_Complete_dataset_without_duplicates_with_categories.csv"), row.names = FALSE)
```
